**Sequencing 16S rRNA gene fragments using the PacBio SMRT DNA sequencing system**

### 2015-12-23 Schloss_PacBio16S_PeerJ_2016.Rmd
Fix formatting

```{r setup, echo=FALSE, eval=TRUE, tidy=TRUE}
rm(list=ls())
library("knitr")
#pdf.options(encoding="ISOLatin2.enc")
regions <- c("v4", "v13", "v35", "v15", "v16", "v19")
clrs <- rainbow(length(regions))
pretty.region <- c("v13"="V1-V3", "v15"="V1-V5", "v16"="V1-V6", "v19"="V1-V9", "v35"="V3-V5", "v4"="V4")
names(clrs) <- regions

opts_chunk$set("fig.path"="figures/")
opts_chunk$set("fig.align"="center")
opts_chunk$set("dev" = c("png", "cairo_pdf"))

opts_chunk$set("tidy" = TRUE)
opts_chunk$set("echo" = FALSE)
opts_chunk$set("eval" = TRUE)
opts_chunk$set("results" = 'hide')
opts_chunk$set("warning" = FALSE)
opts_chunk$set("cache" = TRUE)
```

>>>>

```{r setup, echo=FALSE, eval=TRUE, tidy=TRUE}
regions <- c("v4", "v13", "v35", "v15", "v16", "v19")
clrs <- rainbow(length(regions))
pretty.region <- c("v13"="V1-V3", "v15"="V1-V5", "v16"="V1-V6", "v19"="V1-V9", "v35"="V3-V5", "v4"="V4")
names(clrs) <- regions
```
